---
title: "R Packages for LASSO"
author: Yingyi CHen
date: 2017.10.22
output: ioslides_presentation


---
  
# How to Generate Data
  
## We need to derive "XData" and "YData"  
```{r}
n = 100
p = 500
sigma_noise = 0.5
beta = rep(0, p)
beta[1:6] = c(5,10,3,80,90,10)
XData = matrix(rnorm(n*p,sd=10), nrow = n, ncol=p)
X=XData
for (i in 1:500){
  X[,i]=((X[,i]-sum(X[,i])/n))/((var(X[,i])*99/100)^0.5)
}
YData = X %*% beta + rnorm(n, sd = sigma_noise)
YData=YData-sum(YData)/100
XData=X
```


# Algorithm for LASSO

## Coordinate Descent for LASSO(lambda=0.5)
```{r}
library(homework222)
# Coordinate Descent for LASSO
betaHat1list = chenyingyi11(XData,YData,0.5)
betaHat1=unlist(betaHat1list["betahat"])
diff1 = betaHat1 - beta
# Here we present the L2 loss
L2Losscoordinate = sqrt(sum(diff1^2))
# True Positive Rate
TP1 = sum(abs(beta)>0 & abs(betaHat1)>0) / sum(abs(beta)>0)
# True Negative Rate
TN1 = sum(abs(beta)==0 & abs(betaHat1)==0) / sum(abs(beta)==0)
# Numbers of Iteration
ite1=unlist(betaHat1list["iteration"])
# Values of Objective Function
f1=unlist(betaHat1list["object function"])
```


## Proximal Operator for LASSO(lambda=1)
```{r}
library(homework222)
# Proximal Operator for LASSO
betaHat2list=chenyingyi22(XData, YData, 0.5)
betaHat2 = unlist(betaHat2list["betahat"])
diff2 = betaHat2 - beta
# Here we present the L2 loss
L2Lossproximal = sqrt(sum(diff2^2))
# True Positive Rate
TP2 = sum(abs(beta)>0 & abs(betaHat2)>0) / sum(abs(beta)>0)
# True Negative Rate
TN2 = sum(abs(beta)==0 & abs(betaHat2)==0) / sum(abs(beta)==0)
# Numbers of Iteration
ite2=unlist(betaHat2list["iteration"])
# Values of Objective Function
f2=unlist(betaHat2list["object function"])
```
---

## Compare two algorithms
- The "X-axis" represents iterations
- The "Y-axis" represents log10 values of objective function
- The red line is for Proximal Operator 
- The black line is for Coordinate Descent
```{r}
# log 10 Values of Objective Funcion
f01=log10(f1[1:ite1])
f02=log10(f2[1:ite2])
```

---
```{r}
#lambda=0.5
#plot log10 values of object functions
#numbers of iteration
plot(1:ite2,f02,xlab="iteration",
     ylab="log object function",
     main="Coordinate Descent VS Proximal Operator ",
     type="s",col=2)
lines(1:ite1,f01,col=1)
legend("topright",inset=0.05,
       c("Proximal Operator","Coordinate Descent"),
       lty=c(1,1),col=c("red","black"))
```
--- 
# Conclusion
## Conclusion for lambda=0.5
- Coordinate Descent has less L2 loss but they will all be in TP and TN